Optimal (Multiway) Spatial Joins

### 2024-05-19 msj.tex
yufei

>>>>

\subsection{Previous Results} \label{sec:intro:prev}

SJs have been extensively studied in the database system , which has led to the development of numerous interesting methods that, although lacking strong theoretical guarantees, demonstrate excellent empirical performance on real-world applications. We refer the interested readers to \cite{mp01,???} as entry points into the literature.
